Eleven years of student replication projects provide evidence on the correlates of replicability in psychology

### 2023-04-04 paper/manuscript.Rmd
update cite list

circle back to the idea that student replications (either as class or before extension into their own work) would be valuable 
# Citation slush pile

@@

Anderson, C., Bahnik, S., Barnett-Cowan, M., Bosco, F., Chandler, J., Chartier, C., & otherss. (2016). Response to comment on “estimating the reproducibility of psychological science.” Science, 351(6277), 1037–1037.

Gilbert, D. T., King, G., Pettigrew, S., & Wilson, T. D. (2016). Comment on “estimating the reproducibility of psychological science.” Science, 351(6277), 1037–1037.

Schmidt, S. (2009). Shall we really do it again? The powerful concept of replication is neglected in the social sciences. Review of General Psychology, 13, 90–100.

Simonsohn, U. (2015). Small telescopes: Detectability and the evaluation of replication results. Psychol. Sci., 26(5), 559–569.

Gelman, A. (2018). Don’t characterize replications as successes or failures. Behavioral and Brain Sciences, 41.

Mathur, M. B., & VanderWeele, T. J. (2020a). New statistical metrics for multisite replication projects. J. R. Stat. Soc. Ser. A Stat. Soc., 183(3), 1145–1166.

pedagogy for replication in intro: frank & saxe, hawkins et al., quintana nature paper, scarcity PNAS pedagogy paper,

Collaborative replications and education project (CREP)
JE Grahe, MJ Brandt, H IJzerman, N Legate, J Wagge, YJ Weisberg, BJ Wiggins, Retrieved from osf. io/wfc6u, 2016 - Cited by 29

https://psycnet.apa.org/record/2022-15361-001
https://journals.sagepub.com/doi/pdf/10.1177/1475725719868149
https://content.iospress.com/articles/education-for-information/efi190308

https://psycnet.apa.org/fulltext/2018-11647-005.html

# introduction

@@

replication rates are low in psychology (see studies)

@@

All models used a horseshoe prior in brms. All models will include random slopes for predictors nested within years of the class (year) to control for variation between cohorts of students. We did not include any interaction terms in the models. All numeric predictor variables were z-scored after other transforms (e.g., logs) to ensure comparable regularization effects from the horseshoe prior.

@@

Results of more models in supplement. TODO

@@

# (APPENDIX) Appendices {-}

<!-- The above header does not appear in output. Not exactly sure why. -->

# Appendix A {-}

Some appendix text.

# Appendix B {-}

More appendix text.

>>>>

circle back to the idea that student replications (either as class or before extension into their own work) would be valuable

# Citation slush pile

@@

@gilbert2016 @anderson2016 people argue a lot about how to interpret RPP

@schmidt2009 early theory of replication as part of advancing knowledge

@simonsohn2015 small telescopes

@gelman2018 Don’t characterize replications as successes or failures.

@mathur2020 other metrics of replicability

pedagogy for replication in intro:

@frank2012
@hawkins

@odonnell2021 reps of some set of related things

@wagge2019 get UGs to do replications for

@quintana2021 do reps as honors thesis
@pownall2021 sips 2021 on teaching openness
@jekel2020 teach open science w/ replication 
@jern2018 in one study didn't show critical thinking benefits for students to make them do replications

# introduction
Replicability is a desirable feature for any study that we build theory or future experiments off of. It's a pre-requisite for building theories that we have phenomena for these studies to explain, but results that cannot be observed consistently aren't results to build theories around. However, to be a load-bearing empirical result, a study needs to do much more than just replicate, it also needs to be interesting, have a believable theoretical interpretation, generalize appropriately, and have reliable constructs.

@@

The replication rates in psychology are low, and 
replication rates are low in psychology (see studies)

@@

All models used a horseshoe prior in brms. All models included random slopes for predictors nested within year the class occurred to control for variation between cohorts of students. We did not include any interaction terms in the models. All numeric predictor variables were z-scored after other transforms (e.g., logs) to ensure comparable regularization effects from the horseshoe prior.

@@

Results from these models not reported in the main paper are reported in the supplement.

@@
